Scikit-learn: API design for machine learning

### 2013-06-19 paper.tex
clustering example figure
XXX the float actually makes it take more space, even though the font
is smaller and even without the caption.
Is there a smarter way to keep it from crossing the page boundary?

Some unsupervised learning
estimators may however also implement the \texttt{predict} interface.
The code in Figure~\ref{kmeans-predict} fits a $k$-means model with $k=10$
on training data \texttt{X\_train},
then uses the model's \texttt{predict} method
to obtain cluster labels for unseen data \texttt{X\_test}.

@@

km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
\caption{Finding closest centroids for unseen data after $k$-means clustering.
         \texttt{clust\_pred} will hold integer indices of centroids.}
\label{kmeans-predict}
\end{figure}

>>>>

Some unsupervised learning
estimators may also implement the \texttt{predict} interface.
The code in Figure~\ref{kmeans-predict} fits a $k$-means model with $k=10$
on training data \texttt{X\_train},
then uses the model's \texttt{predict} method
to obtain cluster labels (integer indices) for unseen data \texttt{X\_test}.

@@

km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{pythoncode}
\caption{Finding closest centroids for unseen data after $k$-means clustering.}
\label{kmeans-predict}
\end{figure}
